Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2016-04-02 Paper Sigatoka - 2015.tex
2016-04-01 noche

SVR uses the $\epsilon$-insensitive loss function:
\begin{equation*}
l= {\left| y - f(s) \right| }_{\epsilon } = 
\begin{cases}
   0 & {\left| y - f(s) \right| } \leq \epsilon \\
   \left| y - f(s) \right| - \epsilon & \text{otherwise}
\end{cases}
\end{equation*}
which ignores the error if the difference between the prediction value and the actual value is smaller than $\epsilon$.
%
The $\epsilon$-insensitive loss function allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability.
%
In SVR, the empirical error is measured by the loss function $\epsilon$-insensitive and the generalization ability is measured by the Euclidean norm of $w$ \citep{XXXX201X}.
%
Then, the optimization problem to identify the regression model can be
formulated by \citep{Wei2013}: \marginnote{Falta completar la cita
  XXXXX con el libro de SVR}

@@

A related work, proposed by Romero \citep{Romero1995} relies on regression models using a stepwise procedure to predict incubation and latency times of black Sigatoka. The author performed experiments on two farms located in Costa Rica (La Rita and Waldeck, the same as those used in this study but with different names). The study used data from: December 1993 to August 1995. Romero concluded that the model to predict the incubation period accounted a $R^2$ of 69\% in his observed data but it was not a good predictor when it was validated against an independent dataset (cross validation). For latency, he developed two models that accounted a $R^2$ of 78\% in the observed data, however, when validated against an independent dataset (cross validation), the model was incorrect \hl{PONER EL VALOR OBTENIDO} for Weldeck, and for Rita obtained an adjusted $R^2$ of 82\%.

@@

In the second phase, the best configurations obtained in phase one are used to validate with the last 52 and 102 weeks.

@@

We use the python programming language with the Integrated Development Environment (IDE) Spyder \citep{Continuum2015}, particularly with the libraries pandas \citep{mckinneypandas2010} and numpy \citep{vanderWalt2011}. For SVR, ridge and ordinary least squares regressions, we used sklearn \citep{scikitlearn2011} and for ESN the python-based code of Dr. $Luko\breve{s} evi \breve{c} ius$ \citep{Lukose2012} on which the necessary were done for adjustments for the experiments of this work. The computer used a processor Intel(R) Core™ i7-4800MQ CPU @ 2.70GHz, 16.0 GB RAM, running Windows 8 Pro.

@@

\figurename $.$\ref{figura7} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$. The Rita obtains upper $R^2$ with respect to 28 Millas, but 28 Millas obtains better RMSE than La Rita.

@@

\figurename $.$\ref{figura8} shows the best $R^2$ for each algorithm in the experiment. Results are group by farm.

@@

\figurename $.$\ref{figura9} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm.

@@

\figurename $.$\ref{figura10} shows the best $R^2$ for each variables combination. Results are group by farm.

@@

\figurename $.$\ref{figura11} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$.

@@

\section{Conclusions}

@@

\bibitem[Libro SVM XXXX, 201X]{XXXX201X} Libro SVM XXXX.

>>>>

SVR uses the $\epsilon$-insensitive loss function:
\begin{equation*}
l= {\left| y - f(s) \right| }_{\epsilon } = 
\begin{cases}
   0 & {\left| y - f(s) \right| } \leq \epsilon \\
   \left| y - f(s) \right| - \epsilon & \text{otherwise}
\end{cases}
\end{equation*}
which ignores the error if the difference between the prediction value and the actual value is smaller than $\epsilon$.
%
The $\epsilon$-insensitive loss function allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability.
%
In SVR, the empirical error is measured by the loss function $\epsilon$-insensitive and the generalization ability is measured by the Euclidean norm of $w$ \citep{Cristiani2005}.
%
Then, the optimization problem to identify the regression model can be
formulated by \citep{Wei2013}:

@@

A related work, proposed by Romero \citep{Romero1995} relies on regression models using a stepwise procedure to predict incubation and latency times of black Sigatoka. The author performed experiments on two farms located in Costa Rica (La Rita and Waldeck, the same as those used in this study but with different names). The study used data from: December 1993 to August 1995. Romero concluded that the model to predict the incubation period accounted a $R^2$ of 69\% in his observed data but it was not a good predictor when it was validated against an independent dataset (cross validation). For latency, he developed two models that accounted a $R^2$ of 78\% in the observed data, however, when validated against an independent dataset (cross validation), for La Rita obtained an adjusted $R^2$ of 82\%, and for Weldeck, none of the models satisfactorily predicted the latent period; and then those predictions were not shown \citep{Romero1995}.

@@

In the second phase, the best configurations obtained in phase one are used to validate with the last 50 and 100 weeks.

@@

We use the python programming language with the Integrated Development Environment (IDE) Spyder \citep{Continuum2015}, particularly with the libraries pandas \citep{mckinneypandas2010} and numpy \citep{vanderWalt2011}. For SVR, ridge and ordinary least squares regressions, we used sklearn \citep{scikitlearn2011} and for ESN the python-based code of Dr. $Luko\breve{s} evi \breve{c} ius$ \citep{Lukose2012} on which the necessary were done for adjustments for the experiments of this work. The computer used a processor Intel(R) Core i7-4800MQ CPU 2.70GHz, 16.0 GB RAM, running Windows 8 Pro.

@@

\figurename $.$\ref{figura7} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$. The Rita obtains upper $R^2$ with respect to 28 Millas, but 28 Millas obtains better $RMSE$ than La Rita. This situation arise because $RMSE$ considers errors only with respect the prediction and in 28 Millas the average of Stage of Evolution is $4316.16$, unlike, in La Rita the average is $5507.30$. So, in La Rita we obtains higher errors in absolute values. $R2$ is a relative metric between 0 thru 1 and it is less sensitive to absolute values.

@@

\figurename $.$\ref{figura8} shows the best $R^2$ for each algorithm in the experiment. Results are group by farm. Even if linear models continue with good $R^2$, Echo State Networks improve their scores because in $50$ and $100$ last weeks validation, we are in presence of climate change, then the behaviour is less lineal.

@@

\figurename $.$\ref{figura9} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm. The results confirms that, in general, to predict one week ahead is better than two weeks ahead, two than three and so on, this for both farms.

@@

\figurename $.$\ref{figura10} shows the best $R^2$ for each variables combination. Results are group by farm. This results confirm that $\overline{T}_{a}$ and the combination of $\overline{T}_{a}$ with $\overline{W}$, in both farms are the best variables combinations.

@@

\figurename $.$\ref{figura11} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$.  You can note that the behaviour of $R^2$ and $RMSE$ is similar to the phase one.

@@

Again, similar to phase one, we can conclude that the best configuration in both farms is to consider the climate and the evolution stage of the current week to predict the evolution stage of the next week, one week to predict one week ahead with combinations of variables listed above.

\section{Acknowledgements}

The authors would like to thank Corbana S.A. for providing the data for this research.

@@

\bibitem[Cristiani and Shave-Taylor, 2005]{Cristiani2005} Cristiani, Nello and Shave-Taylor, John. An introduction to support vector machines and other kernel-based learning methods. Cambridge University Press. Ninth printing, United Kingdom, 2005.
